---
title: "Hello R"
author: "Oumayma Ben Aoun"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

- datasaurus_dozen_wide has 142 rows and zero columns (columns are not stated in datasaurus_dozen_wide file)

- There are 26 variables in the datasaurus_dozen_wide file: 

```
away_x: x-values for the away dataset

away_y: y-values for the away dataset

bullseye_x: x-values for the bullseye dataset

bullseye_y: y-values for the bullseye dataset

circle_x: x-values for the circle dataset

circle_y: y-values for the circle dataset

dino_x: x-values for dinosaur dataset!

dino_y: y-values for dinosaur dataset!

dots_x: x-values for the dots dataset

dots_y: y-values for the dots dataset

h_lines_x: x-values for the h_lines dataset

h_lines_y: y-values for the h_lines dataset

high_lines_x: x-values for the high_lines dataset

high_lines_y: y-values for the high_lines dataset

slant_down_x: x-values for the slant_down dataset

slant_down_y: y-values for the slant_down dataset

slant_up_x: x-values for the slant_up dataset

slant_up_y: y-values for the slant_up dataset

star_x: x-values for the star dataset

star_y: y-values for the star dataset

v_lines_x: x-values for the v_lines dataset

v_lines_y: y-values for the v_lines dataset

wide_lines_x: x-values for the wide_lines dataset

wide_lines_y: y-values for the wide_lines dataset

x_shape_x: x-values for the x_shape dataset

x_shape_y: y-values for the x_shape dataset

```


### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```
dino_data %>%
  summarize(r = cor(x, y))
## # A tibble: 1 x 1
## r
## <dbl>
## 1 -0.0645
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, remember to clean up the narrative by removing these instructions.)



```{r plot-star}


```

I'm some text, you should replace me with more meaningful text...
 
```{r cor-star}


```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
